Evaluating Covid-19 Short-Term Forecasts using \pkg{scoringutils} in \proglang{R}

### 2021-03-02 article.Rnw
update paper with scores table and update plots

%% another package (only for this demo article)
\usepackage{framed}

@@

@@

combined <- merge_pred_and_obs(uk_forecasts, covid_uk_data)
@
% 
Before we start with scoring the forecasts, it makes sense to start the evaluation process by visualising the data. To get a feeling for how complete the data set is, we can run the following code to obtain a heatmap with the number of available forecasts: 
% 
\begin{figure}[h]
\centering
<<show-availability, echo=TRUE, fig=TRUE, height=6.7, width=12>>=
show_avail_forecasts(combined, 
                     x = "creation_date", 
                     show_numbers = FALSE,
                     legend_position = "bottom",
                     facet_formula = ~ value_desc)
@
\caption{\label{fig:avail-forecasts} Overview of the number of forecasts available}
\end{figure}
%THINK ABOUT WHETHER THIS FUNCTION CAN BE COMBINED WITH THE OTHER HEATMAP FUNCTION. 
% 
Missing forecasts can have a large impact on the forecast evaluation, if forecasts are not missing at random, but instead missingness correlates with performance. By default, the function treats a set of different quantiles or samples as one forecast. However, the user can specify manually which elements to treat as one forecast and which categories to sum over to count the number of available forecasts.

Forecasts can be visualised using the \fct{plot\_predictions} function. The function accepts either a single combined data set or two separate truth data sets that can be merged together. Forecasts and observed values can be filtered independently, to show for example only predictions from a certain model or a specific number of weeks of true data before the forecast. Conditions to filter on need to be provided as a list of strings, where each of the strings represents an expression that can be evaluated to filter the data. To obtain, for example, a specific forecast from a model we are interest in, we can call: 
% 
\begin{figure}[h!]
\centering
<<show-forecasts, echo=TRUE, fig=TRUE, height=5.2, width=7>>=
locations <- 'c("Scotland", "Wales", "Northern Ireland", "England")'
plot_predictions(truth = covid_uk_data,
                 forecasts = uk_forecasts,
                 filter_both = list(paste("geography %in%", locations, collapse = "")),
                 filter_truth = list('value_date <= "2020-06-22"',
                                     'value_date > "2020-06-01"'), 
                 filter_forecasts = list('model == "SIRCOVID"', 
                                         'creation_date == "2020-06-22"'),
                 x = "value_date",
                 facet_formula = geography ~ value_type) + 
  ggplot2::theme(legend.position = "bottom")
@
\caption{\label{fig:forecast-visualisation} Short-term forecasts made by the SIRCOVID model on June 22 2020.}
\end{figure}
% 
The output is shown in Figure \ref{fig:forecast-visualisation}.

@@

As a first start for the evaluation of UK short-term forecasts, it makes sense to look at the scores achieved by every model separate for all prediction targets. This can be achieved by calling
% 
<<scoring>>=
scores <- eval_forecasts(combined, 
                         summarise_by = c("model", "value_desc"))

@@

<<pairwise-comparison>>=
# unsummarised scores
unsummarised_scores <- eval_forecasts(combined)
pairwise <- pairwise_comparison(unsummarised_scores, 
                                summarise_by = "value_desc")
@

@@

\begin{figure}[h]
\centering
<<score-table, echo=TRUE, fig=TRUE, height=7.2, width=14>>=
score_table(scores, y = "model", facet_formula = ~ value_desc)
@
\caption{\label{fig:score-table} Coloured table to visualise the computed scores}
\end{figure}

@@

\begin{figure}[h!]
\centering
<<pairwise-plot, echo=TRUE, fig=TRUE, height=7.2, width=14>>=
plot_pairwise_comparison(pairwise) +
  ggplot2::facet_wrap(~ value_desc, scales = "free_x") 
@
\caption{\label{fig:pairwise-comparison} Ratios of mean scores based on overlapping forecast sets. If a tile is blue, then the model on the y-axis performed better. If it is red, the model on the x-axis performed better in direct comparison. }
\end{figure}

we can also look at p-values in Figure \ref{fig:pairwise-comparison-pval} PROBABLY REMOVE THAT FROM THE PAPER
\begin{figure}[h!]
\centering
<<pairwise-plot-ratio, echo=TRUE, fig=TRUE, height=7.2, width=14>>=
plot_pairwise_comparison(pairwise, type = "pval") +
  ggplot2::facet_wrap(~ value_desc, scales = "free_x") 
@
\caption{\label{fig:pairwise-comparison-pval} XXXX}
\end{figure}

Both plots can be combined in one: PLOT NEEDS FIXING AND ALSO PROBABLY REMOVE THAT FROM THE PAPER? Figure \ref{fig:pairwise-comparison-both}
\begin{figure}[h!]
\centering
<<pairwise-plot-pval, echo=TRUE, fig=TRUE, height=5.2, width=12>>=
plot_pairwise_comparison(pairwise, type = "together") +
  ggplot2::facet_wrap(~ value_desc, scales = "free_x") 
@
\caption{\label{fig:pairwise-comparison-both} p-values and ratios together.}
\end{figure}

@@

\begin{figure}[h!]
\centering
<<WIS-components, echo=TRUE, fig=TRUE, height=5.2, width=12>>=
wis_components(scores, 
               facet_formula = ~ value_desc, 
               scales = "free_x") + 
  ggplot2::coord_flip() + 
  ggplot2::theme(legend.position = "bottom")
@
\caption{\label{fig:wis-components} p-values and ratios together.}
\end{figure}

@@

\begin{figure}[h!]
\centering
<<coverage, echo=TRUE, fig=TRUE, height=5.2, width=14, out.width = '0.4\\linewidth', fig.show='hold'>>=
cov_scores <- eval_forecasts(combined, 
                             summarise_by = c("model", 
                                              "range", "quantile"))
scoringutils::interval_coverage(cov_scores)
scoringutils::quantile_coverage(cov_scores)
@

<<quantile-coverage, echo=TRUE, fig=TRUE, height=5.2, width=14, out.width = '0.4\\linewidth', fig.show='hold'>>=
cov_scores <- eval_forecasts(combined, 
                             summarise_by = c("model", 
                                              "range", "quantile"))
scoringutils::quantile_coverage(cov_scores)
@

@@

\begin{figure}[h]
\centering
<<calibration, echo=TRUE, fig=TRUE, height=5.2, width=15>>=
scores <- eval_forecasts(combined, 
                         summarise_by = c("model",
                                          "value_desc", 
                                          "geography"), 
                         compute_relative_skill = FALSE)
scoringutils::score_heatmap(scores, metric = "bias", 
                            x = "geography", facet_formula = ~ value_desc, 
                            scale = "free_x")
@
\caption{\label{fig:bias-heatmap} bias by location}
\end{figure}

>>>>

%% another package (only for this demo article)
\usepackage{booktabs}
\usepackage{adjustbox}
\usepackage{tabularx}
\usepackage{rotating}

@@

Table:

\input{tables/scores-table.tex}

@@

combined <- merge_pred_and_obs(uk_forecasts, covid_uk_data)
@
% 
Before we start with scoring the forecasts, it makes sense to start the evaluation process by visualising the data. To get a feeling for how complete the data set is, we can run the following code to obtain a heatmap with the number of available forecasts: 
% 
\begin{figure}[h]
\centering
<<show-availability, echo=TRUE, fig=TRUE, height=6.7, width=12, eval = FALSE>>=
show_avail_forecasts(combined, 
                     x = "creation_date", 
                     show_numbers = FALSE,
                     legend_position = "bottom",
                     facet_formula = ~ value_desc)
@
\caption{\label{fig:avail-forecasts} Overview of the number of forecasts available}
\end{figure}
%THINK ABOUT WHETHER THIS FUNCTION CAN BE COMBINED WITH THE OTHER HEATMAP FUNCTION. 
% 
Missing forecasts can have a large impact on the forecast evaluation, if forecasts are not missing at random, but instead missingness correlates with performance. By default, the function treats a set of different quantiles or samples as one forecast. However, the user can specify manually which elements to treat as one forecast and which categories to sum over to count the number of available forecasts.

Forecasts can be visualised using the \fct{plot\_predictions} function. The function accepts either a single combined data set or two separate truth data sets that can be merged together. Forecasts and observed values can be filtered independently, to show for example only predictions from a certain model or a specific number of weeks of true data before the forecast. Conditions to filter on need to be provided as a list of strings, where each of the strings represents an expression that can be evaluated to filter the data. To obtain, for example, a specific forecast from a model we are interest in, we can call: 
% 
\begin{figure}[h!]
\centering
<<show-forecasts, echo=TRUE, fig=TRUE, height=5.2, width=7, eval = FALSE>>=
locations <- 'c("Scotland", "Wales", "Northern Ireland", "England")'
plot_predictions(truth = covid_uk_data,
                 forecasts = uk_forecasts,
                 filter_both = list(paste("geography %in%", locations, collapse = "")),
                 filter_truth = list('value_date <= "2020-06-22"',
                                     'value_date > "2020-06-01"'), 
                 filter_forecasts = list('model == "SIRCOVID"', 
                                         'creation_date == "2020-06-22"'),
                 x = "value_date",
                 facet_formula = geography ~ value_type) + 
  ggplot2::theme(legend.position = "bottom")
@
\caption{\label{fig:forecast-visualisation} Short-term forecasts made by the SIRCOVID model on June 22 2020.}
\end{figure}
% 
The output is shown in Figure \ref{fig:forecast-visualisation}.

@@

As a first start for the evaluation of UK short-term forecasts, it makes sense to look at the scores achieved by every model separate for all prediction targets. This can be achieved by calling
% 
<<scoring, eval = FALSE>>=
scores <- eval_forecasts(combined, 
                         summarise_by = c("model", "value_desc"))

@@

<<pairwise-comparison, eval = FALSE>>=
# unsummarised scores
unsummarised_scores <- eval_forecasts(combined)
pairwise <- pairwise_comparison(unsummarised_scores, 
                                summarise_by = "value_desc")
@

@@

\begin{figure}[h]
\centering
<<score-table, echo=TRUE, fig=TRUE, height=7.2, width=14, eval = FALSE>>=
score_table(scores, y = "model", facet_formula = ~ value_desc)
@
\caption{\label{fig:score-table} Coloured table to visualise the computed scores}
\end{figure}

@@

\begin{figure}[h!]
\centering
<<pairwise-plot, echo=TRUE, fig=TRUE, height=7.2, width=14, eval = FALSE>>=
plot_pairwise_comparison(pairwise) +
  ggplot2::facet_wrap(~ value_desc, scales = "free_x") 
@
\caption{\label{fig:pairwise-comparison} Ratios of mean scores based on overlapping forecast sets. If a tile is blue, then the model on the y-axis performed better. If it is red, the model on the x-axis performed better in direct comparison. }
\end{figure}

we can also look at p-values in Figure \ref{fig:pairwise-comparison-pval} PROBABLY REMOVE THAT FROM THE PAPER
\begin{figure}[h!]
\centering
<<pairwise-plot-ratio, echo=TRUE, fig=TRUE, height=7.2, width=14, eval = FALSE>>=
plot_pairwise_comparison(pairwise, type = "pval") +
  ggplot2::facet_wrap(~ value_desc, scales = "free_x") 
@
\caption{\label{fig:pairwise-comparison-pval} XXXX}
\end{figure}

@@

\begin{figure}[h!]
\centering
<<WIS-components, echo=TRUE, fig=TRUE, height=5.2, width=12, eval = FALSE>>=
wis_components(scores, 
               facet_formula = ~ value_desc, 
               scales = "free_x") + 
  ggplot2::coord_flip() + 
  ggplot2::theme(legend.position = "bottom")
@
\caption{\label{fig:wis-components} p-values and ratios together.}
\end{figure}

@@

\begin{figure}[h!]
\centering
<<coverage, echo=TRUE, fig=TRUE, height=5.2, width=14, out.width = '0.4\\linewidth', fig.show='hold', eval = FALSE>>=
cov_scores <- eval_forecasts(combined, 
                             summarise_by = c("model", 
                                              "range", "quantile"))
scoringutils::interval_coverage(cov_scores)
scoringutils::quantile_coverage(cov_scores)
@

<<quantile-coverage, echo=TRUE, fig=TRUE, height=5.2, width=14, out.width = '0.4\\linewidth', fig.show='hold', eval = FALSE>>=
cov_scores <- eval_forecasts(combined, 
                             summarise_by = c("model", 
                                              "range", "quantile"))
scoringutils::quantile_coverage(cov_scores)
@

@@

\begin{figure}[h]
\centering
<<calibration, echo=TRUE, fig=TRUE, height=5.2, width=15, eval = FALSE>>=
scores <- eval_forecasts(combined, 
                         summarise_by = c("model",
                                          "value_desc", 
                                          "geography"), 
                         compute_relative_skill = FALSE)
scoringutils::score_heatmap(scores, metric = "bias", 
                            x = "geography", facet_formula = ~ value_desc, 
                            scale = "free_x")
@
\caption{\label{fig:bias-heatmap} bias by location}
\end{figure}

### 2021-03-02 article.tex
update paper with scores table and update plots

We first need to obtain the data by installing and loading the \pkg{covid19.forecasts.uk} using the following commands: 
% 
\begin{Schunk}
\begin{Sinput}
R> # install and load data pacakge from external repository
R> # remotes::install_github("sbfnk/covid19.forecasts.uk")
R> 
R> # load packages
R> library(covid19.forecasts.uk)
R> library(dplyr)
R> library(scoringutils)
R> # load truth data
R> data(covid_uk_data)
R> # head(covid_uk_data)
R> 
R> # load forecasts
R> data(uk_forecasts)
R> # head(uk_forecasts)
\end{Sinput}
\end{Schunk}
% 
Let us take a first look a the data:
% 
\begin{Schunk}
\begin{Sinput}
R> glimpse(covid_uk_data)
\end{Sinput}
\begin{Soutput}
Rows: 4,174
Columns: 6
$ geography  <fct> London, London, London, London, London, London, …
$ value_type <fct> hospital_inc, hospital_inc, hospital_inc, hospit…
$ value_desc <fct> Hospital admissions, Hospital admissions, Hospit…
$ truncation <dbl> 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, …
$ value_date <date> 2020-03-20, 2020-03-21, 2020-03-22, 2020-03-23,…
$ value      <dbl> 18, 232, 280, 241, 313, 353, 516, 637, 677, 546,…
\end{Soutput}
\begin{Sinput}
R> glimpse(uk_forecasts)
\end{Sinput}
\begin{Soutput}
Rows: 1,254,513
Columns: 8
$ model         <fct> EpiSoon, EpiSoon, EpiSoon, EpiSoon, EpiSoon, …
$ geography     <chr> "East of England", "East of England", "East o…
$ value_type    <fct> hospital_inc, hospital_inc, hospital_inc, hos…
$ creation_date <date> 2020-03-31, 2020-03-31, 2020-03-31, 2020-03-…
$ value_date    <date> 2020-04-01, 2020-04-02, 2020-04-03, 2020-04-…
$ quantile      <dbl> 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.0…
$ value         <dbl> 70, 64, 53, 42, 30, 19, 4, 0, 0, 0, 0, 0, 0, …
$ value_desc    <fct> Hospital admissions, Hospital admissions, Hos…
\end{Soutput}
\end{Schunk}
% 
To bring the forecasts into the format needed for the evaluation, some minor changes need to be made to the data. The names of the columns that hold the forecasts and the true observed values need to be changed to \code{prediction} and \code{true_value}. While we could also proceed with separate data sets for the evaluation, we merge the two data sets in order to remove all instances where the forecasts, but not the true observations were made public. The \pkg{scoringutils} package provides a function that attempts to merge the data sets in a sensible way. 
% 
\begin{Schunk}
\begin{Sinput}
R> uk_forecasts <- rename(uk_forecasts, prediction = value)
R> covid_uk_data <-rename(covid_uk_data, true_value = value)
R> combined <- merge_pred_and_obs(uk_forecasts, covid_uk_data)
\end{Sinput}
\end{Schunk}
% 
Before we start with scoring the forecasts, it makes sense to start the evaluation process by visualising the data. To get a feeling for how complete the data set is, we can run the following code to obtain a heatmap with the number of available forecasts: 
% 
\begin{figure}[h]
\centering
\begin{Schunk}
\begin{Sinput}
R> show_avail_forecasts(combined, 
+                       x = "creation_date", 
+                       show_numbers = FALSE,
+                       legend_position = "bottom",
+                       facet_formula = ~ value_desc)
\end{Sinput}
\end{Schunk}
\includegraphics{plots/plot-show-availability}
\caption{\label{fig:avail-forecasts} Overview of the number of forecasts available}
\end{figure}
%THINK ABOUT WHETHER THIS FUNCTION CAN BE COMBINED WITH THE OTHER HEATMAP FUNCTION. 
% 
Missing forecasts can have a large impact on the forecast evaluation, if forecasts are not missing at random, but instead missingness correlates with performance. By default, the function treats a set of different quantiles or samples as one forecast. However, the user can specify manually which elements to treat as one forecast and which categories to sum over to count the number of available forecasts.

Forecasts can be visualised using the \fct{plot\_predictions} function. The function accepts either a single combined data set or two separate truth data sets that can be merged together. Forecasts and observed values can be filtered independently, to show for example only predictions from a certain model or a specific number of weeks of true data before the forecast. Conditions to filter on need to be provided as a list of strings, where each of the strings represents an expression that can be evaluated to filter the data. To obtain, for example, a specific forecast from a model we are interest in, we can call: 
% 
\begin{figure}[h!]
\centering
\begin{Schunk}
\begin{Sinput}
R> locations <- 'c("Scotland", "Wales", "Northern Ireland", "England")'
R> plot_predictions(truth = covid_uk_data,
+                   forecasts = uk_forecasts,
+                   filter_both = list(paste("geography %in%", locations, collapse = "")),
+                   filter_truth = list('value_date <= "2020-06-22"',
+                                       'value_date > "2020-06-01"'), 
+                   filter_forecasts = list('model == "SIRCOVID"', 
+                                           'creation_date == "2020-06-22"'),
+                   x = "value_date",
+                   facet_formula = geography ~ value_type) + 
+    ggplot2::theme(legend.position = "bottom")
\end{Sinput}
\end{Schunk}
\includegraphics{plots/plot-show-forecasts}
\caption{\label{fig:forecast-visualisation} Short-term forecasts made by the SIRCOVID model on June 22 2020.}
\end{figure}
% 
The output is shown in Figure \ref{fig:forecast-visualisation}.

@@

As a first start for the evaluation of UK short-term forecasts, it makes sense to look at the scores achieved by every model separate for all prediction targets. This can be achieved by calling
% 
\begin{Schunk}
\begin{Sinput}
R> scores <- eval_forecasts(combined, 
+                           summarise_by = c("model", "value_desc"))
R> glimpse(scores)
\end{Sinput}
\begin{Soutput}
Rows: 29
Columns: 11
$ model              <chr> "EpiSoon", "StructuredODE", "Microsimula…
$ value_desc         <fct> Hospital admissions, Hospital admissions…
$ interval_score     <dbl> 38.56510, 61.75914, 100.71914, 35.44876,…
$ sharpness          <dbl> 22.886153, 6.133974, 33.985553, 10.36508…
$ underprediction    <dbl> 3.66782766, 24.82255866, 33.12350598, 8.…
$ overprediction     <dbl> 12.0111222, 30.8026045, 33.6100814, 16.5…
$ coverage_deviation <dbl> 0.034531405, -0.268749094, -0.095652174,…
$ bias               <dbl> 0.26194170, -0.27368253, -0.39217045, -0…
$ aem                <dbl> 45.96333, 73.38096, 138.14395, 53.22563,…
$ relative_skill     <dbl> 0.9085917, 1.2479010, 0.7405995, 0.82232…
$ scaled_rel_skill   <dbl> NaN, NaN, NaN, NaN, NaN, NaN, NaN, NaN, …
\end{Soutput}
\end{Schunk}
% 
If a more detailed analysis is desired, the level of aggregation can of course be changed to show for example separate scores for the different locations as well. This can be achieved using the \code{summarise_by} argument. To additionally stratify by location, we could specify \code{summarise_by = c("mode", "value_type", "geography")}. If we wanted to have one score per quantile or one per prediction interval range, we could specify something like \code{summarise_by = c("model", "quantile")} or \code{summarise_by = c("model", "quantile", "range")}. This can be useful if we, for example, want to analyse what proportion of true values are covered by certain interval ranges, or if we want to analyse the accuracy of the tails of the forecasts. When aggregating, \fct{eval\_forecasts} takes the mean according to the group defined in \code{summarise_by}. In the above example, if \code{summarise_by = c("model", "value_type")}, then scores would be averaged over all creation dates, forecast horizons (as represented by the the value dates), locations and quantiles to yield one score per model and forecast target. In addition to the mean, we can also obtain the standard deviation of the scores over which we average, as well as any desired quantile, by specifying \code{sd = TRUE} and for example \code{quantiles = c(0.5)} for the median.

@@

\begin{figure}[h]
\centering
\begin{Schunk}
\begin{Sinput}
R> score_table(scores, y = "model", facet_formula = ~ value_desc)
\end{Sinput}
\end{Schunk}
\includegraphics{plots/plot-score-table}
\caption{\label{fig:score-table} Coloured table to visualise the computed scores}
\end{figure}

@@

\begin{figure}[h!]
\centering
\begin{Schunk}
\begin{Sinput}
R> plot_pairwise_comparison(pairwise) +
+    ggplot2::facet_wrap(~ value_desc, scales = "free_x") 
\end{Sinput}
\end{Schunk}
\includegraphics{plots/plot-pairwise-plot}
\caption{\label{fig:pairwise-comparison} Ratios of mean scores based on overlapping forecast sets. If a tile is blue, then the model on the y-axis performed better. If it is red, the model on the x-axis performed better in direct comparison. }
\end{figure}

we can also look at p-values in Figure \ref{fig:pairwise-comparison-pval} PROBABLY REMOVE THAT FROM THE PAPER
\begin{figure}[h!]
\centering
\begin{Schunk}
\begin{Sinput}
R> plot_pairwise_comparison(pairwise, type = "pval") +
+    ggplot2::facet_wrap(~ value_desc, scales = "free_x") 
\end{Sinput}
\end{Schunk}
\includegraphics{plots/plot-pairwise-plot-ratio}
\caption{\label{fig:pairwise-comparison-pval} XXXX}
\end{figure}

Both plots can be combined in one: PLOT NEEDS FIXING AND ALSO PROBABLY REMOVE THAT FROM THE PAPER? Figure \ref{fig:pairwise-comparison-both}
\begin{figure}[h!]
\centering
\begin{Schunk}
\begin{Sinput}
R> plot_pairwise_comparison(pairwise, type = "together") +
+    ggplot2::facet_wrap(~ value_desc, scales = "free_x") 
\end{Sinput}
\end{Schunk}
\includegraphics{plots/plot-pairwise-plot-pval}
\caption{\label{fig:pairwise-comparison-both} p-values and ratios together.}
\end{figure}

@@

\begin{figure}[h!]
\centering
\begin{Schunk}
\begin{Sinput}
R> wis_components(scores, 
+                 facet_formula = ~ value_desc, 
+                 scales = "free_x") + 
+    ggplot2::coord_flip() + 
+    ggplot2::theme(legend.position = "bottom")
\end{Sinput}
\end{Schunk}
\includegraphics{plots/plot-WIS-components}
\caption{\label{fig:wis-components} p-values and ratios together.}
\end{figure}

@@

\begin{figure}[h!]
\centering
\begin{Schunk}
\begin{Sinput}
R> cov_scores <- eval_forecasts(combined, 
+                               summarise_by = c("model", 
+                                                "range", "quantile"))
R> scoringutils::interval_coverage(cov_scores)
R> scoringutils::quantile_coverage(cov_scores)
\end{Sinput}
\end{Schunk}
\includegraphics{plots/plot-coverage}

\begin{Schunk}
\begin{Sinput}
R> cov_scores <- eval_forecasts(combined, 
+                               summarise_by = c("model", 
+                                                "range", "quantile"))
R> scoringutils::quantile_coverage(cov_scores)
\end{Sinput}
\end{Schunk}
\includegraphics{plots/plot-quantile-coverage}

@@

\begin{figure}[h]
\centering
\begin{Schunk}
\begin{Sinput}
R> scores <- eval_forecasts(combined, 
+                           summarise_by = c("model",
+                                            "value_desc", 
+                                            "geography"), 
+                           compute_relative_skill = FALSE)
R> scoringutils::score_heatmap(scores, metric = "bias", 
+                              x = "geography", facet_formula = ~ value_desc, 
+                              scale = "free_x")
\end{Sinput}
\end{Schunk}
\includegraphics{plots/plot-calibration}
\caption{\label{fig:bias-heatmap} bias by location}
\end{figure}

>>>>

We first need to obtain the data by installing and loading the \pkg{covid19.forecasts.uk} using the following commands: 
% 
\begin{Schunk}
\begin{Sinput}
R> # install and load data pacakge from external repository
R> # remotes::install_github("sbfnk/covid19.forecasts.uk")
R> 
R> # load packages
R> library(covid19.forecasts.uk)
R> library(dplyr)
R> library(scoringutils)
R> # load truth data
R> data(covid_uk_data)
R> # head(covid_uk_data)
R> 
R> # load forecasts
R> data(uk_forecasts)
R> # head(uk_forecasts)
\end{Sinput}
\end{Schunk}
% 
Let us take a first look a the data:
% 
\begin{Schunk}
\begin{Sinput}
R> glimpse(covid_uk_data)
\end{Sinput}
\begin{Soutput}
Rows: 4,174
Columns: 6
$ geography  <fct> London, London, London, London, London, London, …
$ value_type <fct> hospital_inc, hospital_inc, hospital_inc, hospit…
$ value_desc <fct> Hospital admissions, Hospital admissions, Hospit…
$ truncation <dbl> 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, …
$ value_date <date> 2020-03-20, 2020-03-21, 2020-03-22, 2020-03-23,…
$ value      <dbl> 18, 232, 280, 241, 313, 353, 516, 637, 677, 546,…
\end{Soutput}
\begin{Sinput}
R> glimpse(uk_forecasts)
\end{Sinput}
\begin{Soutput}
Rows: 1,254,513
Columns: 8
$ model         <fct> EpiSoon, EpiSoon, EpiSoon, EpiSoon, EpiSoon, …
$ geography     <chr> "East of England", "East of England", "East o…
$ value_type    <fct> hospital_inc, hospital_inc, hospital_inc, hos…
$ creation_date <date> 2020-03-31, 2020-03-31, 2020-03-31, 2020-03-…
$ value_date    <date> 2020-04-01, 2020-04-02, 2020-04-03, 2020-04-…
$ quantile      <dbl> 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.0…
$ value         <dbl> 70, 64, 53, 42, 30, 19, 4, 0, 0, 0, 0, 0, 0, …
$ value_desc    <fct> Hospital admissions, Hospital admissions, Hos…
\end{Soutput}
\end{Schunk}
% 
To bring the forecasts into the format needed for the evaluation, some minor changes need to be made to the data. The names of the columns that hold the forecasts and the true observed values need to be changed to \code{prediction} and \code{true_value}. While we could also proceed with separate data sets for the evaluation, we merge the two data sets in order to remove all instances where the forecasts, but not the true observations were made public. The \pkg{scoringutils} package provides a function that attempts to merge the data sets in a sensible way. 
% 
\begin{Schunk}
\begin{Sinput}
R> uk_forecasts <- rename(uk_forecasts, prediction = value)
R> covid_uk_data <-rename(covid_uk_data, true_value = value)
R> combined <- merge_pred_and_obs(uk_forecasts, covid_uk_data)
\end{Sinput}
\end{Schunk}
% 
Before we start with scoring the forecasts, it makes sense to start the evaluation process by visualising the data. To get a feeling for how complete the data set is, we can run the following code to obtain a heatmap with the number of available forecasts: 
% 
\begin{figure}[h]
\centering
\begin{Schunk}
\begin{Sinput}
R> show_avail_forecasts(combined, 
+                       x = "creation_date", 
+                       show_numbers = FALSE,
+                       legend_position = "bottom",
+                       facet_formula = ~ value_desc)
\end{Sinput}
\end{Schunk}
\caption{\label{fig:avail-forecasts} Overview of the number of forecasts available}
\end{figure}
%THINK ABOUT WHETHER THIS FUNCTION CAN BE COMBINED WITH THE OTHER HEATMAP FUNCTION. 
% 
Missing forecasts can have a large impact on the forecast evaluation, if forecasts are not missing at random, but instead missingness correlates with performance. By default, the function treats a set of different quantiles or samples as one forecast. However, the user can specify manually which elements to treat as one forecast and which categories to sum over to count the number of available forecasts.

Forecasts can be visualised using the \fct{plot\_predictions} function. The function accepts either a single combined data set or two separate truth data sets that can be merged together. Forecasts and observed values can be filtered independently, to show for example only predictions from a certain model or a specific number of weeks of true data before the forecast. Conditions to filter on need to be provided as a list of strings, where each of the strings represents an expression that can be evaluated to filter the data. To obtain, for example, a specific forecast from a model we are interest in, we can call: 
% 
\begin{figure}[h!]
\centering
\begin{Schunk}
\begin{Sinput}
R> locations <- 'c("Scotland", "Wales", "Northern Ireland", "England")'
R> plot_predictions(truth = covid_uk_data,
+                   forecasts = uk_forecasts,
+                   filter_both = list(paste("geography %in%", locations, collapse = "")),
+                   filter_truth = list('value_date <= "2020-06-22"',
+                                       'value_date > "2020-06-01"'), 
+                   filter_forecasts = list('model == "SIRCOVID"', 
+                                           'creation_date == "2020-06-22"'),
+                   x = "value_date",
+                   facet_formula = geography ~ value_type) + 
+    ggplot2::theme(legend.position = "bottom")
\end{Sinput}
\end{Schunk}
\caption{\label{fig:forecast-visualisation} Short-term forecasts made by the SIRCOVID model on June 22 2020.}
\end{figure}
% 
The output is shown in Figure \ref{fig:forecast-visualisation}.

@@

As a first start for the evaluation of UK short-term forecasts, it makes sense to look at the scores achieved by every model separate for all prediction targets. This can be achieved by calling
% 
\begin{Schunk}
\begin{Sinput}
R> scores <- eval_forecasts(combined, 
+                           summarise_by = c("model", "value_desc"))
R> glimpse(scores)
\end{Sinput}
\end{Schunk}
% 
If a more detailed analysis is desired, the level of aggregation can of course be changed to show for example separate scores for the different locations as well. This can be achieved using the \code{summarise_by} argument. To additionally stratify by location, we could specify \code{summarise_by = c("mode", "value_type", "geography")}. If we wanted to have one score per quantile or one per prediction interval range, we could specify something like \code{summarise_by = c("model", "quantile")} or \code{summarise_by = c("model", "quantile", "range")}. This can be useful if we, for example, want to analyse what proportion of true values are covered by certain interval ranges, or if we want to analyse the accuracy of the tails of the forecasts. When aggregating, \fct{eval\_forecasts} takes the mean according to the group defined in \code{summarise_by}. In the above example, if \code{summarise_by = c("model", "value_type")}, then scores would be averaged over all creation dates, forecast horizons (as represented by the the value dates), locations and quantiles to yield one score per model and forecast target. In addition to the mean, we can also obtain the standard deviation of the scores over which we average, as well as any desired quantile, by specifying \code{sd = TRUE} and for example \code{quantiles = c(0.5)} for the median.

@@

\begin{figure}[h]
\centering
\begin{Schunk}
\begin{Sinput}
R> score_table(scores, y = "model", facet_formula = ~ value_desc)
\end{Sinput}
\end{Schunk}
\caption{\label{fig:score-table} Coloured table to visualise the computed scores}
\end{figure}

@@

\begin{figure}[h!]
\centering
\begin{Schunk}
\begin{Sinput}
R> plot_pairwise_comparison(pairwise) +
+    ggplot2::facet_wrap(~ value_desc, scales = "free_x") 
\end{Sinput}
\end{Schunk}
\caption{\label{fig:pairwise-comparison} Ratios of mean scores based on overlapping forecast sets. If a tile is blue, then the model on the y-axis performed better. If it is red, the model on the x-axis performed better in direct comparison. }
\end{figure}

we can also look at p-values in Figure \ref{fig:pairwise-comparison-pval} PROBABLY REMOVE THAT FROM THE PAPER
\begin{figure}[h!]
\centering
\begin{Schunk}
\begin{Sinput}
R> plot_pairwise_comparison(pairwise, type = "pval") +
+    ggplot2::facet_wrap(~ value_desc, scales = "free_x") 
\end{Sinput}
\end{Schunk}
\caption{\label{fig:pairwise-comparison-pval} XXXX}
\end{figure}

@@

\begin{figure}[h!]
\centering
\begin{Schunk}
\begin{Sinput}
R> wis_components(scores, 
+                 facet_formula = ~ value_desc, 
+                 scales = "free_x") + 
+    ggplot2::coord_flip() + 
+    ggplot2::theme(legend.position = "bottom")
\end{Sinput}
\end{Schunk}
\caption{\label{fig:wis-components} p-values and ratios together.}
\end{figure}

@@

\begin{figure}[h!]
\centering
\begin{Schunk}
\begin{Sinput}
R> cov_scores <- eval_forecasts(combined, 
+                               summarise_by = c("model", 
+                                                "range", "quantile"))
R> scoringutils::interval_coverage(cov_scores)
R> scoringutils::quantile_coverage(cov_scores)
\end{Sinput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
R> cov_scores <- eval_forecasts(combined, 
+                               summarise_by = c("model", 
+                                                "range", "quantile"))
R> scoringutils::quantile_coverage(cov_scores)
\end{Sinput}
\end{Schunk}

@@

\begin{figure}[h]
\centering
\begin{Schunk}
\begin{Sinput}
R> scores <- eval_forecasts(combined, 
+                           summarise_by = c("model",
+                                            "value_desc", 
+                                            "geography"), 
+                           compute_relative_skill = FALSE)
R> scoringutils::score_heatmap(scores, metric = "bias", 
+                              x = "geography", facet_formula = ~ value_desc, 
+                              scale = "free_x")
\end{Sinput}
\end{Schunk}
\caption{\label{fig:bias-heatmap} bias by location}
\end{figure}
